|

### 2021-09-24 03-Chp-Systematic-Review.Rmd
Back to a working version

@@

>>>>

<!----------------------------------------------------------------------------->
(ref:mrDuplication-cap) Summary of duplication of MR studies which used similar data from the Global Lipid

(ref:mrDuplication-scap) Summary of duplication of MR studies

```{r mrDuplicationSetup, include=FALSE}
```

```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
```
<!----------------------------------------------------------------------------->

@@

A key example of the importance of pleiotropy in Mendelian randomisations studies is ill. In almost all cases, MR studies examine. A clear exampe of this is Ben et al, 2017, where the ApoE variants were not sufficient identified and excluded, and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated this finding towards the null.[@benn2017a]
